---
title: "SimmsFishFence"
author: "Eric V"
date: "`r Sys.Date()`"
output: bookdown::html_document2
  
#   html_notebook: 
#     toc: yes
#   flexdashboard::flex_dashboard:
#     orientation: columns
#     vertical_layout: scroll  
#   html_document:
#     fig_caption: true
#     code_folding: "show"
#     toc: true
#     toc_float: true
# editor_options: 
#   chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Intro

Simms Creek is a small, 3rd order stream that drains an area of \~1,800 ha into the Salish Sea, near Campbell River's Willow Point neighborhood. The lower reach of Simms Creek (\~3 km of channel, east of Jubilee Road), is contained within a narrow urban green way that is bordered by residential properties. From Jubilee Road to the Inland Highway the stream is protected within [Beaver Lodge Lands](https://campbellriver.travel/news/forestry-guide-to-beaver-lodge-lands/), upstream of the Inland Highway, \>1.5 km of tributary channel is located within private forest lands.

Historic fish observations indicate that Chum, Chinook, Pink and Coho Salmon have all been observed in the stream, as well as Coastal Cutthroat Trout, Rainbow Trout and Steelhead. Recent records, this dataset, suggest that Coho Salmon and Coastal Cutthroat Trout are the primary species within Simms Creek, both of which utilize the stream year round - though a small number of juvenile Chinook Salmon were identified in 2024.

[Greenways Land Trust](https://www.greenwaystrust.ca/) has supported Simms Creek Stewards for +20 years, including operation of a fish fence near the mouth of the stream since 2008. Juvenile and adult fish moving past the fence are tallied each spring and fall, respectively. The objective of this project is to explore the juvenile fence dataset. All work is being done strictly for fun and out of personal curiosity. Any feedback, input, or support is welcome. Also, I have a soft spot for Coastal Cutthroat Trout (CCT), so be warned that all analysis will be trout heavy.

```{r Prep working environment, echo=FALSE, warning=FALSE, message = FALSE}
## Clear workspace ##
rm(list = ls())  

## This code is to fix a bug in R 2023.06.0+421 <https://github.com/rstudio/rstudio/issues/13188>
    options(rstudio.help.showDataPreview = FALSE)
    # getOption("rstudio.help.showDataPreview")

## Load Packages and dependencies. 
list.of.packages <- c("tidyverse",
                      "purrr",
                      "tidyr",
                      "dplyr",
                      "scales",
                      "lubridate",
                      "reshape2",
                      "ggplot2",
                      "readxl",
                      "openxlsx",
                      "downloadthis",
                      "knitr",
                      "captioner",
                      "zoo",
                      "gridExtra",
                      "plotly",
                      "htmlwidgets",
                      "shiny")

  ## Load any missing packages.
    new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
    if(length(new.packages)) install.packages(new.packages)

## Load Packages
    library(tidyverse)
    library(purrr)
    library(tidyr)
    library(dplyr)
    library(lubridate)
    library(reshape2)
    library(ggplot2)
    library(scales)
    library(readxl)
    library(openxlsx)
    library(downloadthis)
    library(knitr)
    library(captioner)
    library(zoo)
    library(gridExtra)
    library(plotly)
    library(htmlwidgets)
    library(formattable)
    library(xfun)
    library(kableExtra)
    library(shiny)
    
##  Set up captioner package calls. 
  fig_nums   <- captioner(prefix = "Figure")  
  table_nums <- captioner(prefix = "Table")

## Define Working Directory ---
# setwd("C:/Users/evogt/R Analysis/EAV/GitHubMarkdown/SimmsCreek/docs")
```

```{r Load and Format Data, echo = FALSE, warning = FALSE, message = FALSE}
# Load Juvenile and Adult Bio Data ----
   data_sets <- c("Juvenile","Adult")

      for(i in data_sets){
            #1.1 List of all files in Directory 
            files_list <- list.files(paste0("Data/",i ,"/"), pattern = "*.xlsx", full.names = TRUE)
            
                # Use lapply to read in all files and store them as list elements in one list
                list_of_dfs <- lapply(as.list(files_list), function(x) readWorkbook(x, sheet = "SimmsBioData"))
        
                # Create a vector of names based on the year of data collection. 
                df_names2 <- paste0(i,"_SimmsBio_", as.numeric(str_extract(files_list, "(\\d)+")))
                
                # Assign the names to our list of dfs
                names(list_of_dfs) <- df_names2
          
          #1.2 Dunno what this does...
           dfs_list <-lapply(list_of_dfs, "[")
               # my_cols <- c("Date", "Species", "Stage", "US/DS", "Length", "Weight", "Comments")
         
          #1.3 Prepare final dataframe
          df <-   bind_rows(dfs_list, .id = "Dataset")
          
             ## Rename dataframe based on looping variable (e.g., Juvenile or Adult)
             assign(paste("simms_bio_",i, sep=""), df) %>%
              mutate(MonitorPeriod = i)
      }

    ### Format Juvenile Data ----
    juv <- simms_bio_Juvenile %>%
           mutate(Period = "Spring",
                  Sex = "",
                  DatasetYear = as.numeric(str_extract(Dataset, "(\\d)+")),
                  Date = as.Date(Date, origin = "1899-12-30"),
                  Year = as.numeric(format(Date, format = "%Y"))) %>%
           filter(DatasetYear == Year) %>%                                          # Filter to exclude relic data from past years
           rename(Direction = "US/DS") %>%
           select("Dataset","Period", "Date", "Species", "Stage","Sex", "Direction", "Length", "Weight", "Comments")

    ### Format Adult Data ----
    adult <- simms_bio_Adult %>%
             mutate(Period = "Fall",
                    Stage = "",
                    DatasetYear = as.numeric(str_extract(Dataset, "(\\d)+")),
                    Date = as.Date(Date, origin = "1899-12-30"),
                    Year = as.numeric(format(Date, format = "%Y"))) %>%
             filter(DatasetYear == Year) %>%                                          # Filter to exclude relic data from past years
             rename(Direction = "US/DS") %>%
             select("Dataset","Period","Date", "Species", "Stage","Sex", "Direction", "Length", "Weight", "Comments")

      ### Join Juvenile and Adult Datasets ----
          simms_bio_all <- rbind(juv,adult) %>%
                           mutate(Direction = recode(as.factor(Direction),
                                                   US        = "Upstream",
                                                  'US '      = "Upstream",
                                                   UST       = "Upstream",
                                                   DS        = "Downstream",
                                                  'DS '      = "Downstream",
                                                   DST       = "Downstream"),
                                Species = recode(as.factor(Species),
                                                 "CO"  = "CO",
                                                 "CO " = "CO",
                                                 " CO" = "CO",
                                                 "CO-J"= "CO-J",
                                                 "JK"  = "CO-J",
                                                 "CT"  = "CT",
                                                 "CT " = "CT",
                                                 "CN"  = "CN",
                                                 "CN " = "CN",
                                                 "CH"  = "CN",
                                                 "PK" = "PK"),
                                Species = factor(Species, 
                                                 levels = c("CT","CO", "CO-J","CN","CM","PK")))

# Load Environmental Data ----
      for(i in data_sets){
            #1.1 List of all files in Directory 
            files_list <- list.files(paste0("Data/",i ,"/"), pattern = "*.xlsx", full.names = TRUE)
        
           # files_list <- list.files(paste0("Data/Adult/"), pattern = "*.xlsx", full.names = TRUE)
            
                # Use lapply to read in all files and store them as list elements in one list
                list_of_dfs <- lapply(as.list(files_list), function(x) readWorkbook(x, sheet = "SimmsCreek", cols = 1:10))

                # Create a vector of names based on the year of data collection. 
                df_names2 <- paste0(i,"_SimmsEnv_", as.numeric(str_extract(files_list, "(\\d)+")))
                
                # Assign the names to our list of dfs
                names(list_of_dfs) <- df_names2
          
          #1.2 Dunno what this does...
          # dfs_list <-lapply(list_of_dfs, "[")
            dfs_list <- lapply(list_of_dfs, "[")
          
         
          #1.3 Prepare final dataframe
          df <-   bind_rows(dfs_list, .id = "Dataset") %>%
                     mutate(MonitorPeriod = i)
          
         ## Rename dataframe based on looping variable (e.g., Juvenile or Adult)
         assign(paste("simms_env_",i, sep=""), df) 
      }    
    
    ## Rename simms env. variables
    simms_env_Juvenile <- simms_env_Juvenile %>%
                          rename(pH = "PH",
                                 Gauge = "Staff.Gauge")
    
    #### Join Env. Datasets ----
    simms_env <- rbind(simms_env_Juvenile,simms_env_Adult) %>%
               mutate(Period = ifelse(MonitorPeriod == "Adult","Fall","Spring"),
                      DatasetYear = as.numeric(str_extract(Dataset, "(\\d)+")),
                      Date = as.Date(Date, origin = "1899-12-30"),
                      Time = format(as.POSIXct(Time), "%I:%M %p"),
                      Year = as.numeric(format(Date, format = "%Y")),
                      binary = 1) %>%
               filter(DatasetYear == Year)
    

# Join Bio and Env Data ----
     # Create Date Sequence    
      date_seq <- data.frame(Date = seq(ymd('2008-04-15'), ymd('2024-06-15'), by = 'days')) %>%
                      mutate(Month = strftime(Date, format = "%m"),
                             Month = as.numeric(Month))

    # Join Data to Date Sequence
    all_dat <- left_join(date_seq,simms_env, by = c("Date"), suffix = c("","_Env")) %>%
               left_join(., simms_bio_all, by = c("Date","Period"), suffix = c("","_Bio")) %>%
               mutate(Year = as.numeric(format(Date, format = "%Y")),
                      Period = factor(Period, levels = c("Spring","Fall"))) %>%
               select(Year, Period, Date, Month, Time,    Air.Temp, Water.Temp, 
                      pH,   DO,     TDS,  Gauge, Weather, Species, Length, Weight)
```

# Annual Fence Monitoring Effort
```{r Master Catch Summary, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
# Master Trap Summary ----
## Trap Effort ----
trap_effort <- all_dat %>% 
               group_by(Year, Period, Date) %>%
               summarize(binary = 1) %>%
               ungroup() %>%
               group_by(Year, Period) %>%
               summarize(trap_days = sum(binary),
                         start = min(Date),
                         end   = max(Date)) %>%
               filter(complete.cases(Period))


## Catch by Year and Period ----
    spp <- c("CO", "CT")
    # for loop to summarize CO and CT catch data 
    for(i in spp){
      
        x <- all_dat %>%  
             filter(Species == i) %>%
             group_by(Year, Period, Species) %>%
             summarize(n = n(),
                       n = coalesce(n,0),
                       Date_min = min(Date, na.rm=T),
                       Date_med = median(Date, na.rm=T),
                       Date_max = max(Date, na.rm=T),
                       FL_mean = mean(Length, na.rm = T),
                       FL_min  = min(Length, na.rm = T),
                       FL_max  = max(Length, na.rm = T),
                       FL_SD   = sd(Length, na.rm = T))


          ## Create DFs named "catch_CT" and "catch_CO"
          assign(paste0("catch_", i, sep = ""), x)
    }
    
    catch_summary <- left_join(trap_effort, catch_CT, by = c("Year", "Period"), suffix = c("","_CT")) %>%
                          left_join(.,catch_CO, by = c("Year","Period"), suffix = c("CT","CO")) %>%
                      select("Year", "Period", "start","end", "trap_days", 
                             "nCT", "Date_medCT","Date_minCT", "Date_maxCT", "FL_meanCT", "FL_SDCT", "FL_minCT", "FL_maxCT",
                             "nCO", "Date_medCO","Date_minCO", "Date_maxCO", "FL_meanCO", "FL_SDCO", "FL_minCO", "FL_maxCO") %>%
                      mutate(start = format(start, "%b-%d"),
                             end   = format(end, "%b-%d"),
                             Date_medCT = format(Date_medCT, "%b-%d"),
                             Date_minCT = format(Date_minCT, "%b-%d"),
                             Date_maxCT = format(Date_maxCT, "%b-%d"),
                             Date_medCO = format(Date_medCO, "%b-%d"),
                             Date_minCO = format(Date_minCO, "%b-%d"),
                             Date_maxCO = format(Date_maxCO, "%b-%d")) %>%
                     mutate_at(vars(nCT,nCO), ~replace_na(.,0))
## Kable - Master Summary ----
options(knitr.kable.NA = '-')

kable(catch_summary,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c("Year", "Period", "Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max",
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 1. Trapping summary.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" " = 2, "Sample Period" = 3, 
                     "Capture Timing" = 4,"Fork Length (mm)" = 4,
                     "Capture Timing" = 4,"Fork Length (mm)" = 4)) %>%
  add_header_above(c(" " = 5, "Coastal Cutthroat Trout" = 8, "Coho Salmon" = 8)) 
```


```{r CT Catch Summary, echo=FALSE, warning=FALSE, message = FALSE}
## Prep Data ----
CT_catch <- catch_summary %>%
            select(1:13) %>%  # Select CT Data
            pivot_wider(names_from = Period, values_from = 3:13) %>%
            select(1, ends_with("Spring"), ends_with("Fall")) %>%
            ungroup() %>%
            add_row(Year = c(2020, 2021, 2023)) %>%
            arrange(Year)


## CT Kable ----
kable(CT_catch,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Year","Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max",
                    "Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 1. Spring and Fall Trapping of Coastal Cutthroat Trout.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" "=1, "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4,
                     "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4)) %>%
  add_header_above(c(" " = 1,"Spring" = 11, "Fall" = 11)) 
 
```

```{r}

```



```{r}
catch_long <- all_dat %>%
              group_by(Year, Period, Species) %>%
              summarize(n = n()) %>%
              filter(!is.na(Period),
                     !is.na(Species)) 



ggplot(catch_long) +
  geom_col(aes(x = Year, y = n)) + 
  facet_grid(Species~Period)
```



```{r exit}
knitr::knit_exit()
```


# Annual Fence Monitoring Effort and Catches
```{r, Trap Summary, echo=FALSE, warning=FALSE, message = FALSE}
# When trap was operated
  ## Create Date Sequence - All dates when trap could be checked
  date_seq <- data.frame(Date = seq(ymd('2008-04-15'), ymd('2024-06-15'), by = 'days')) %>%
                  mutate(Month = strftime(Date, format = "%m"),
                         Month = as.numeric(Month)) %>%
                  filter(between(Month,4,6))

  ## Which days trap was operated each year
  trap <- juv %>%
            group_by(Date) %>%
            summarize(n = 1) %>%
            mutate(Year = strftime(Date, format = "%Y"))
  
  ## Proportion of survey period that was monitored.
  trap_ops <- left_join(date_seq, trap, by = "Date") %>%
              mutate(n = coalesce(n, 0)) %>%
              group_by(Year) %>%
              dplyr::summarize(Start = as.Date(min(Date)),
                              End   = as.Date(max(Date)),
                              SamplePeriod = as.numeric((End-Start)+1),
                              DaysSampled = sum(n)) %>%
              mutate(prop.sample.period =  percent(DaysSampled/SamplePeriod),
                     prop.mig.period = percent(DaysSampled/75),
                     Year  = as.numeric(Year),
                     Start = format(Start, "%b-%d"),
                     End   = format(End, "%b-%d"))
  

  

    ## Number of Fish Tallied Annually
  annual_tally <- simms_bio_all %>%
                  ungroup %>%
                  filter(Species == "CO" | Species == "CT") %>%
                  group_by(Year, Species) %>%
                  dplyr::summarise(n = n()) %>%
                  pivot_wider(names_from = "Species", values_from = "n")

## Summary Table
summary_table <- left_join(trap_ops,annual_tally, by = "Year") %>%
                     filter(!is.na(Year)) %>%
                     select(1:3,5:9) %>%
                     mutate(Total = CO + CT)

```

Fence monitoring starts in April and continues through late May to mid June. The first day of trap operation has ranged from `r format(min(as.Date(trap_ops$Start, "%b-%d")),"%b-%d")` to `r format(max(as.Date(trap_ops$Start, "%b-%d")), "%b-%d")` (mean = `r format(mean(as.Date(trap_ops$Start, "%b-%d")),"%b-%d")`). Once monitoring was initiated the traps were checked nearly continuously, with an average of `r round(mean(trap_ops$prop.sample.period),1)` of days being monitored. After a mean of `r round(mean(trap_ops$DaysSampled),0)` days the trap was dismantled and monitoring was ceased between `r format(min(as.Date(trap_ops$End, "%b-%d")),"%b-%d")` and `r format(max(as.Date(trap_ops$End, "%b-%d")),"%b-%d")` (mean = `r format(mean(as.Date(trap_ops$End, "%b-%d")),"%b-%d")`).

Annual trap operation periods and total captures of Coastal Cutthroat Trout and Coho Salmon are presented below in Table 1.

```{r display.table, echo = FALSE, warning = FALSE, message = FALSE}
## Prepare Kable Table
kable(summary_table,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Year", "Start", "End", "# Days Sampled", "Sample Period", "Migration Period", "CO", "CCT", "Total"),
      caption = "**Table 1. Annual trap operation period, proportion of operation period that was monitored, proportion of migration period that was monitored (Apr 1 to June 15), and number of Coho Salmon and Coastal Cutthroat Trout that were tallied.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" " = 1, "Sample Period" = 3, "Prop. Sampled (%)"= 2, "# Fish Tallied" =3)) 
```

```{original table, echo=FALSE, warning=FALSE, message = FALSE }
CCT_table <-  simms_bio %>% 
                group_by(Year, Species) %>%
                dplyr::summarize(
                                 # Start_Date = as.Date(min(Date), "%b-%d"),
                                 # End_Date   = as.Date(max(Date), "%b-%d"),
                                 # Survey_Length = 1+(as.Date(End_Date) - as.Date(Start_Date)),
                                 n          = n(),
                                 FL_mean = mean(Length, na.rm = TRUE),
                                 FL_SD   = sd(Length, na.rm = TRUE),
                                 FL_min  = min(Length, na.rm = TRUE),
                                 FL_max  = max(Length, na.rm = TRUE),
                                 WT_mean = mean(Weight, na.rm = TRUE),
                                 WT_min  = min(Weight, na.rm = TRUE),
                                 WT_max  = max(Weight, na.rm = TRUE)) %>%
                  # mutate(Start_Date = format(Start_Date, "%b-%d"),
                  #        End_Date = format(End_Date, "%b-%d")) %>%
                  #select("Year","Direction", "Start_Date","End_Date","Survey_Length","n","FL_mean","FL_SD","FL_min","FL_max")
                  select(1:11)

## Prepare Kable Table
kable(CCT_table,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Species", "Year", "Direction","Start", "End", "Duration","Total \nCatch", "Mean", "SD", "Min", "Max"),
      caption = "**Table 1. Total annual captures of Coastal Cutthroat Trout during spring fish fence operation on Simms Creek.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" " = 3, "Period" = 3, "","Fork Length (mm)" = 4)) 
```

## Coastal Cutthroat Trout

As previously mentioned, I like CCT, so let's start there. We will look at the size of fish being captured, when the majority of the fish are migrating, and start to consider what may be driving some of the variability in migrants between years.

### Size Distribution

```{r, length-frequency all years,echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of all CCT captured to date.
    ## Prepare Data
    CT_dat <- simms_bio %>% 
                    filter(Species == "CT",
                           !is.na(Direction)) %>%
                    mutate(date.std =  case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
                    

      ## Prepare Plot
      all_years.plot <- ggplot(CT_dat) +
                            geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                            labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                            scale_x_continuous(breaks = seq(50, 450, by = 25))+
                            #scale_y_continuous(breaks = seq(0, 450, 50))+
                            theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                            theme_bw() + 
                            facet_grid(Direction~.)
```

```{r, length-frequency all years PRINT, echo=FALSE, fig.width = 10, fig.height = 7}
suppressWarnings(print(all_years.plot))
```

**`r fig_nums("all_years.plot", "Length-frequency of all Coastal Cutthroat Trout captured since 2008.")`**

```{r, length-frequency by year,  echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of CCT captured in each year
    ## Prepare Data
    annual.plot <- ggplot(CT_dat) +
                        geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                        labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                        scale_x_continuous(breaks = seq(0, 500, by = 20))+
                        #scale_y_continuous(breaks = seq(0, 450, 50))+
                        theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                        theme_bw() + 
                        facet_grid(Year~Direction)
```

```{r, length-frequency by yearPRINT, echo=FALSE, fig.width = 14, fig.height = 35}
suppressWarnings(print(annual.plot))
```

**`r fig_nums("annual.plot", "Length-frequency of Coastal Cutthroat Trout captured during annual monitoring.")`**

### Capture Timing

```{r,  echo=FALSE, warning=FALSE, message = FALSE}
## Prep Data
    ## Catch Data
    CCT_catch <- simms_bio %>% 
                 filter(Species == "CT") %>%
                 group_by(Date, Direction) %>%
                 summarize(catch = n()) %>%
                 mutate(Year = strftime(Date, format = "%Y")) %>%
                 ungroup() %>%
                 group_by(Year) %>%
                 mutate(cum_catch   = cumsum(catch),
                        total_catch = max(cum_catch),
                        prop        = cum_catch/total_catch,
                        date.std    = case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024)))

    # ## Date Sequence
    # date_seq <- data.frame(Date = as.Date(seq(ymd('2008-04-15'), ymd('2025-06-15'), by = 'days'))) %>%
    #                         mutate(Month = strftime(Date, format = "%m"),
    #                                Month = as.numeric(Month)) %>%
    #                         filter(between(Month,4,6))
    #                         
    # 
    # ## Join date_seq w. catch data
    # catch_daily <- left_join(date_seq, CCT_DS, by = "Date") %>%
    #                    mutate(catch = coalesce(catch, 0),  
    #                           Year = strftime(Date, format = "%Y"),
    #                           Year = as.numeric(Year),
    #                           Month = strftime(Date, format = "%m"),
    #                           Month = as.numeric(Month),
    #                           Weeknum = strftime(Date, format = "%V"),
    #                           Weeknum = as.numeric(Weeknum))
    # 
    # ## 
    # CCT_catchDS <- CCT_catch %>% 
    #                filter(Direction == "Downstream") %>%
    #                mutate(date.std = case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
    
    daily_catch <- ggplot(CCT_catch) + 
                      geom_line(aes(x = date.std, y = prop, color = Direction)) +
                      labs(x = "", y = "Proportion of Total Annual Catch") +
                      scale_x_date(date_minor_breaks = "1 day", 
                           date_breaks = '1 week', 
                           date_labels = '%b-%d', 
                           limits = c(as.Date("2024-04-01"), as.Date("2024-06-15"))) +
                      facet_grid(Year~.) +
                      theme(legend.position = "bottom") +
                      theme_bw()

```

```{r, daily_catches, echo=FALSE, fig.width = 10, fig.height = 15}
suppressWarnings(print(daily_catch))
```

**`r fig_nums("daily_catch", "Proportion of total annual upstream and downstream catches.")`**

```{r}
all_catches <- simms_bio %>% 
               group_by(Species, Date, Direction) %>%
               summarize(catch = n()) %>%
               mutate(Year = strftime(Date, format = "%Y")) %>%
               ungroup() %>%
               group_by(Year) %>%
               mutate(cum_catch   = cumsum(catch),
                      total_catch = max(cum_catch),
                      prop        = cum_catch/total_catch,
                      date.std    = case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) %>%
               filter(!is.na(Direction))
    
daily_box <- ggplot(all_catches) + 
                    geom_line(aes(x = date.std, y = catch, color = Species)) +
                    labs(x = "", y = "Proportion of Total Annual Catch") +
                    scale_x_date(date_minor_breaks = "1 day", 
                           date_breaks = '1 week',
                           date_labels = '%b-%d',
                           limits = c(as.Date("2024-04-01"), as.Date("2024-06-15"))) +
                    facet_grid(Year~Direction) +
                    theme(legend.position = "bottom") +
                    theme_bw() 
```

```{r, daily_box, echo=FALSE, fig.width = 10, fig.height = 15}
suppressWarnings(print(daily_box))
```

**`r fig_nums("daily_box", "Boxplot showing range of captures of CCT and CO salmon.")`**

## Coho Salmon
