---
title: "SimmsFishFence"
author: "Eric V"
date: "`r Sys.Date()`"
theme: cerulean
output: 
  
  html_document:
    fig_caption: true
    code_folding: "show"
    toc: true
    toc_float: true
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll  
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

Data presented here was collected by volunteers working with [Greenways Land Trust](https://www.greenwaystrust.ca/) to monitor the number of Coho Salmon and Coastal Cutthroat Trout emigrating from Simms Creek. Monitoring has occurred annually since 2008. No monitoring was completed in 2020 or 2021 due to the COVID pandemic, nor was monitoring completed in 2023 due to a DFO strike. 

## Coastal Cutthroat Trout
```{r prep working environment, echo=FALSE, warning=FALSE, message = FALSE}
## Prepare Working Environment ----
## Clear workspace ##
# rm(list = ls())  

## This code is to fix a bug in R 2023.06.0+421 <https://github.com/rstudio/rstudio/issues/13188>
    options(rstudio.help.showDataPreview = FALSE)
    # getOption("rstudio.help.showDataPreview")

## Load Packages and dependencies. 
list.of.packages <- c("tidyverse",
                      "purrr",
                      "tidyr",
                      "dplyr",
                      "scales",
                      "lubridate",
                      "reshape2",
                      "ggplot2",
                      "readxl",
                      "openxlsx",
                      "downloadthis",
                      "knitr",
                      "captioner",
                      "zoo",
                      "gridExtra",
                      "plotly",
                      "htmlwidgets",
                      "shiny")

  ## Load any missing packages.
    new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
    if(length(new.packages)) install.packages(new.packages)

## Load Packages
    library(tidyverse)
    library(purrr)
    library(tidyr)
    library(dplyr)
    library(lubridate)
    library(reshape2)
    library(ggplot2)
    library(scales)
    library(readxl)
    library(openxlsx)
    library(downloadthis)
    library(knitr)
    library(captioner)
    library(zoo)
    library(gridExtra)
    library(plotly)
    library(htmlwidgets)
    library(formattable)
    library(xfun)
    library(kableExtra)
    library(shiny)
    
##  Set up captioner package calls. 
  fig_nums   <- captioner(prefix = "Figure")  
  table_nums <- captioner(prefix = "Table")

## Define Working Directory ---
   # setwd("C:/Users/evogt/R Analysis/EAV/GitHubMarkdown/Simms/docs")

## Define Input Files
   #1 Load Simms Bio Data from all years
      #1.1 List of all files in Directory 
        files_list <- list.files("Data/", pattern = "*.xlsx", full.names = TRUE)
   
            # Use lapply to read in all files and store them as list elements in one list
                list_of_dfs <- lapply(as.list(files_list), function(x) readWorkbook(x, sheet = "SimmsBioData"))
    
            # Create a vector of names based on the year of data collection. 
                df_names2 <- paste0("SimmsBio_", as.numeric(str_extract(files_list, "(\\d)+")))
                  
            # Assign the names to our list of dfs
                names(list_of_dfs) <- df_names2
                  
      #1.2 Select Columns of Interest
           my_cols <- c("Date", "Species", "Stage", "US/DS", "Length", "Weight", "Comments")
           dfs_list <- lapply(list_of_dfs, "[", my_cols)

    #3 Join all dataframes together
      simms_bio <-   bind_rows(dfs_list, .id = "Dataset") %>%
                        mutate(DatasetYear = as.numeric(str_extract(Dataset, "(\\d)+")),
                               Date = as.Date(Date, origin = "1899-12-30"),
                               Year = as.numeric(format(Date, format = "%Y"))) %>%
                        filter(DatasetYear == Year) %>%                                          # Filter to exclude relic data from past years
                        rename(Direction = "US/DS") %>%
                        mutate(Direction = recode(as.factor(Direction), 
                                         US        = "Upstream",
                                        'US '      = "Upstream",
                                         UST       = "Upstream",
                                         DS        = "Downstream",
                                        'DS '      = "Downstream",
                                         DST       = "Downstream"))
```

### Monitoring Effort and Catches

```{r, data summary, echo=FALSE, warning=FALSE, message = FALSE}
# Summary table of bio data
CCT_table <-  simms_bio %>% filter(Species == "CT") %>%
                group_by(Species, Year, Direction) %>%
                dplyr::summarize(Start_Date = as.Date(min(Date), "%b-%d"),
                                 End_Date   = as.Date(max(Date), "%b-%d"),
                                 Survey_Length = 1+(as.Date(End_Date) - as.Date(Start_Date)),
                                 n          = n(),
                                 FL_mean = mean(Length, na.rm = TRUE),
                                 FL_SD   = sd(Length, na.rm = TRUE),
                                 FL_min  = min(Length, na.rm = TRUE),
                                 FL_max  = max(Length, na.rm = TRUE),
                                 WT_mean = mean(Weight, na.rm = TRUE),
                                 WT_min  = min(Weight, na.rm = TRUE),
                                 WT_max  = max(Weight, na.rm = TRUE)) %>%
                  mutate(Start_Date = format(Start_Date, "%b-%d"),
                         End_Date = format(End_Date, "%b-%d")) %>%
                  #select("Year","Direction", "Start_Date","End_Date","Survey_Length","n","FL_mean","FL_SD","FL_min","FL_max")
                  select(1:11)

## Prepare Kable Table
kable(CCT_table,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Species", "Year", "Direction","Start", "End", "Duration","Total \nCatch", "Mean", "SD", "Min", "Max"),
      caption = "**Table 1. Total annual captures of Coastal Cutthroat Trout during spring fish fence operation on Simms Creek.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" " = 3, "Period" = 3, "","Fork Length (mm)" = 4)) 


```

#### Size Distribution

```{r, length-frequency all years,echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of all CCT captured to date.
    ## Prepare Data
    CT_dat <- simms_bio %>% 
                    filter(Species == "CT",
                           !is.na(Direction)) %>%
                    mutate(date.std =  case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
                    

      ## Prepare Plot
      all_years.plot <- ggplot(CT_dat) +
                            geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                            labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                            scale_x_continuous(breaks = seq(50, 450, by = 25))+
                            #scale_y_continuous(breaks = seq(0, 450, 50))+
                            theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                            theme_bw() + 
                            facet_grid(Direction~.)
```

```{r, length-frequency all years PRINT, echo=FALSE, fig.width = 10, fig.height = 7}
suppressWarnings(print(all_years.plot))
```

**`r fig_nums("all_years.plot", "Length-frequency of all Coastal Cutthroat Trout captured since 2008.")`**


```{r, length-frequency by year,  echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of CCT captured in each year
    ## Prepare Data
    annual.plot <- ggplot(CT_dat) +
                        geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                        labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                        scale_x_continuous(breaks = seq(0, 500, by = 20))+
                        #scale_y_continuous(breaks = seq(0, 450, 50))+
                        theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                        theme_bw() + 
                        facet_grid(Year~Direction)
```
 
```{r, length-frequency by yearPRINT, echo=FALSE, fig.width = 14, fig.height = 35}
suppressWarnings(print(annual.plot))
```

**`r fig_nums("annual.plot", "Length-frequency of Coastal Cutthroat Trout captured during annual monitoring.")`**

### Capture Timing

```{r,  echo=FALSE, warning=FALSE, message = FALSE}
## Prep Data
    ## Catch Data
    CCT_catch <- simms_bio %>% 
                 filter(Species == "CT") %>%
                 group_by(Date, Direction) %>%
                 summarize(catch = n()) %>%
                 mutate(Year = strftime(Date, format = "%Y")) %>%
                 ungroup() %>%
                 group_by(Year) %>%
                 mutate(cum_catch   = cumsum(catch),
                        total_catch = max(cum_catch),
                        prop        = cum_catch/total_catch,
                        date.std    = case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024)))

    # ## Date Sequence
    # date_seq <- data.frame(Date = as.Date(seq(ymd('2008-04-15'), ymd('2025-06-15'), by = 'days'))) %>%
    #                         mutate(Month = strftime(Date, format = "%m"),
    #                                Month = as.numeric(Month)) %>%
    #                         filter(between(Month,4,6))
    #                         
    # 
    # ## Join date_seq w. catch data
    # catch_daily <- left_join(date_seq, CCT_DS, by = "Date") %>%
    #                    mutate(catch = coalesce(catch, 0),  
    #                           Year = strftime(Date, format = "%Y"),
    #                           Year = as.numeric(Year),
    #                           Month = strftime(Date, format = "%m"),
    #                           Month = as.numeric(Month),
    #                           Weeknum = strftime(Date, format = "%V"),
    #                           Weeknum = as.numeric(Weeknum))
    # 
    # ## 
    # CCT_catchDS <- CCT_catch %>% 
    #                filter(Direction == "Downstream") %>%
    #                mutate(date.std = case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
    
    daily_catch <- ggplot(CCT_catch) + 
                      geom_line(aes(x = date.std, y = prop, color = Direction)) +
                      labs(x = "", y = "Proportion of Total Annual Catch") +
                      scale_x_date(date_minor_breaks = "1 day", 
                           date_breaks = '1 week', 
                           date_labels = '%b-%d', 
                           limits = c(as.Date("2024-04-01"), as.Date("2024-06-15"))) +
                      facet_grid(Year~.) +
                      theme(legend.position = "bottom") +
                      theme_bw()
```

```{r, daily_catches, echo=FALSE, fig.width = 10, fig.height = 15}
suppressWarnings(print(daily_catch))
```

**`r fig_nums("daily_catch", "Proportion of total annual upstream and downstream catches.")`**

## Coho Salmon
