---
title: "SimmsFishFence"
author: "Eric V"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
    highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
    fig_caption: true
    code_folder: show
    smart: true
    toc: true
    toc_float: 
      toc_depth: 1
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll 
  html_notebook:
    toc: yes  


#bibliography: biobliography.bib
    
---

```{r old yaml, include = FALSE}


# <!--   flexdashboard::flex_dashboard: -->
# <!--     orientation: columns -->
# <!--     vertical_layout: scroll -->
# <!--   html_notebook: -->
# <!--     toc: true -->
# <!--   word_document: -->
# <!--     toc: true -->
# <!-- editor_options: -->
# <!--   chunk_output_type: inline -->
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

# 1. Introduction

Simms Creek is a small, 3rd order stream that drains an area of \~1,800 ha into the Salish Sea, near Campbell River's Willow Point neighborhood. The lower reach of Simms Creek (\~3 km of channel, east of Jubilee Road), is contained within a narrow urban green way that is bordered by residential properties. From Jubilee Road to the Inland Highway the stream is protected within [Beaver Lodge Lands](https://campbellriver.travel/news/forestry-guide-to-beaver-lodge-lands/), upstream of the Inland Highway, \>1.5 km of tributary channel is located within private forest lands.

Historic fish observations indicate that Chum, Chinook, Pink and Coho salmon have all been observed in the stream, as well as Coastal Cutthroat Trout (CCT), Rainbow Trout and steelhead. More recent monitoring (i.e., this dataset), suggest that Coho Salmon (CO) and CCT are the primary species within Simms Creek, both of which utilize the stream year round - though a small number of juvenile Chinook Salmon were identified in 2024.

[Greenways Land Trust](https://www.greenwaystrust.ca/) has supported Simms Creek Stewards for +20 years, including operation of a fish fence near the mouth of the stream since 2008. Juvenile and adult fish moving past the fence are tallied each spring and fall, respectively. The objective of this project is to explore the juvenile fence dataset. All work is being done strictly for fun and out of personal curiosity. Any feedback, input, or support is welcome. Also, I have a soft spot for CCT, so be warned that effort and results will be slightly trout biased.

Throughout this analysis, I will aim to answer the following questions:

1.  What species are utilizing Simms Creek?

2.  Is the current fence operation program capturing the complete migration period?

3.  For each species, when are key behaviours occurring (e.g., when is peak smolt? when do adults arrive?).

4.  How large are fish encountered during smolt and upstream migration periods? What age classes are migrating (I don't have scale data, but we can make an educated guess).

5.  What is the freshwater survival of Coho Salmon? Note that we cannot estimate marine survival without some information on individual fish (i.e., coded wire tag data to verify that returning adults originated in Simms Creek and when they smolted).

<!-- 6.  What proportion of returning Coho Salmon are hatchery origin? Have any hatchery origin trout been encountered (not actually sure if there are many hatchery reared trout at the moment, and if so, if they are marked). -->

7.  What factors may be contributing to observed trends in abundance?

But before we can do that, lets take a look at what has been completed to date. It's a tremendous amount of work and all volunteers and supporters should be commended!

```{r 1. Load and Format Data, echo = FALSE, warning = FALSE, message = FALSE}
## Clear workspace ##
# rm(list = ls())  

# ## Load Prepped Data
 # source("SourceFiles/0. RunSourceFiles.R")
# 
  source("SourceFiles/1. Load and Prep Data.R")
# 
# ## Load Trap Effort Data
 source("SourceFiles/2. Trapping Effort.R")

```

# 2. Spring Fence Operation

### 2.1. Monitoring Effort {.tabset .tabset-dropdown}
The Simms Creek fish fence has operated annually since 2008, with the exception of 2020 and 2021 when operations were paused due to the COVID-19 Pandemic and in the spring of 2023 when federal employees were on strike.

Spring surveys target out migrating juvenile Coho Salmon but also capture an impressive number of CCT and have even captured some Chinook Salmon. Spring fence monitoring has started as early as `r format(min(trap_plot$date.std[trap_plot$Period=="Spring"]), "%B %d")`, however, most surveys (50%) don't start until `r format(min(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled >= 0.5]), "%B %d")`. In each monitoring year, the fence has operated continuously (e.g., sampling occurred at least daily) from `r format(min(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled == 1.0]), "%B %d")` to `r format(max(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled == 1.0]), "%B %d")`. Surveys have continued as late as `r format(max(trap_plot$date.std[trap_plot$Period=="Spring"]), "%B %d")`, but most (50%) are terminated by `r format(max(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled==0.5]), "%B %d")`.

#### Monitoring Effort Tables and Figures

#### Table 1. Spring Sampling Summary
```{r 2. Trap Effort Summary Table , fig.cap = "Table 1. Summary of Spring Sampling Effort.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE}
xy <- trap_effort_summary_table %>% filter(Period == "Spring")

kable(xy,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c("Period","Min","Max", "Mean", "SD",
                             "Min","Max", "Mean", "SD",
                             "Min","Max", "Mean", "SD"),
      caption = "Table 1. Annual spring and fall trap operation periods.",
      digits = 1) %>%
    
      kable_styling("striped", full_width =  FALSE,
                      position = "center", 
                      font_size = 12,
                      fixed_thead = TRUE) %>%
        add_header_above(c(" " = 1, "# Days Sampled" = 4, "Start Date" = 4, "End Date"=4))

```


#### Table 2. Annual Spring and Fall Trap Operation Periods
```{r 2. Trap Effort Table trap effort table, fig.cap = "Table 2. Annual spring and fall trap operation periods.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE}

trap_effort_spring <- trap_effort_table %>% select(1:4)

## Kable - Master Summary ----
options(knitr.kable.NA = '-')
    

    kable(trap_effort_spring,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c("Year", "# Days Sampled", "Start", "End"), 
      #                     "# Days Sampled", "Start", "End"),
      caption = "Table 1. Annual spring and fall trap operation periods.",
      
      digits = 1) %>%
  # column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE)
  # add_header_above(c(" " = 1, "Spring Sampling" = 3, "Fall Sampling" = 3))
```





#### Figure 1. Spring sampling period. 

```{r 2. Trap Effort - Fall Plot, fig.cap = "Figure 1. Fall adult trapping effort, presented as the proportion of sample years when trapping was completed on each date.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 15, fig.height = 5, }

print(trap_effort_plot_fall)

```

<!-- **`r fig_nums("fall.trap.plot", "Fall trap operation period, presented as the proportion of sample years each date has been trapped since 2008 (excluding years when trapping did not occur due to COVID or government strikes).")`** -->



```{r 3. Stream Conditions - Load Data, echo=FALSE, warning=FALSE, message = FALSE}

## Load Stream Conditions Data 
 source("SourceFiles/3. Stream Conditions.R")

```

### 2.2 Stream Conditions {.tabset .tabset-dropdown}

During each daily trap visit, volunteers record measures of water temperature, pH, Total Suspended Sediment (TSS), dissolved oxygen, and water level (stage). Mean annual measures of each parameter are presented below for the Spring monitoring period (Table 2 and Figure 3). 

#### Stream Conditions Figures and Tables

#### Table 3. Spring Condition Table
```{r 3. Stream Conditions - Spring Table, fig.cap = "Table 3. Overall annual stream conditions during spring trap monitoring from 2008 to 2024.", fig.topcaption = TRUE,echo=FALSE, warning=FALSE, message = FALSE}

cond_data_wide.spring <- cond_data_wide %>% select(1:13)

## Kable - Stream Conditions ----
options(knitr.kable.NA = '-')
    

    kable(cond_data_wide.spring,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c(" ", "Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD"),
      caption = "Table 2. Stream conditions during spring trap operation.",
      
      digits = 1) %>%
  column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>% 
  add_header_above(c(" " = 1, "Air Temp. \n(\u00B0C)" = 2, "Water Temp. \n(\u00B0C)" = 2, 
                              "pH \n. " = 2, "DO \n(mg/L)" = 2, "TDS \n(ppm)" = 2, "Water Level \n(m)" = 2)) %>%
  add_header_above(c("Year"= 1, "Spring Monitoring" = 12))    

```

#### Figure 2. Spring Condition Plot
```{r 3. Stream Conditions - Plot, fig.cap = "Figure 2. Average daily measures of air and water temperature, pH, dissolved oxygen (DO), total dissolved solids (TDS) and water level (stage).", echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 15, fig.topcaption = TRUE}

print(cond_plot)
```

### 2.3. Annual Captures {.tabset .tabset-dropdown}
```{r 4. Fish Captures - Summary Table catch_dat.prep, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
source("SourceFiles/4. Annual Captures.R")
```

Since 2008, a total of `r format(sum(catch_annual.Table.Spring$nCT), big.mark =",")` juvenile CCT and `r format(sum(catch_annual.Table.Spring$nCO), big.mark =",")` juvenile Coho Salmon have been captured during spring trapping. Annual captures of CCT have ranged from `r format(min(catch_annual.Table.Spring$nCT), big.mark =",")` to `r format(max(catch_annual.Table.Spring$nCT), big.mark =",")` (mean = `r format(mean(catch_annual.Table.Spring$nCT), digits = 1)`) while CO captures have varied from `r format(min(catch_annual.Table.Spring$nCO), big.mark =",")` to `r format(max(catch_annual.Table.Spring$nCO), big.mark =",")` with an overall mean of `r format(mean(catch_annual.Table.Spring$nCO), digits = 1)` fish (Figure 3 and Table 4).

#### Annual Captures Figures and Tables

#### Figure 3. Total annual catches
```{r 4. Annual Captures - Summary Plot, fig.cap = "Figure 3. Total annual catch of CCT and Coho Salmon during Spring fence monitoring.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12}

print(catch_annual_barPlot.Spring)
```
#### Table 4. Total Annual Catches
```{r Annual Captures - SummaryTable, echo=FALSE, warning=FALSE, message = FALSE}
## Kable - Master Summary ----
options(knitr.kable.NA = '-')

kable(catch_annual.Table.Spring,
      "html",
      booktabs = T,
      
      align = c("c"),
      # col.names = c("Year", "Period", "Start", "End", "# Days Sampled", 
      col.names = c("Year", "Start", "End", "# Days Sampled",  
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max",
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 4. Spring capture summary - capture timing, total captures and length of CCT and Coho Salmon.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  # add_header_above(c(" " = 2, "Sample Period" = 3, 
  add_header_above(c(" " = 1, "Sample Period" = 3,                   
                     "Capture Timing" = 3,"Fork Length (mm)" = 5,
                     "Capture Timing" = 3,"Fork Length (mm)" = 5)) %>%
  add_header_above(c(" " = 4, "CCT" = 8, "Coho Salmon" = 8)) 
```



### 2.4. Migration Timing {.tabset .tabset-dropdown}
```{r 5. Capture Timing - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/5. Capture Timing.R")
```

```{r 5. Capture Timing - Prepare text values, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE }

CT.first.detection.earliest <- format(min(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"]), "%B %d")
CT.first.detection.latest   <- format(max(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"]), "%B %d")
CT.first.detection.mean     <- format(mean(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"], na.rm = TRUE), "%B %d")
CT.first.detection.SD       <- round(sd(pass.period.spring$minMeanDiff[pass.period.spring$Species=="CT"], na.rm = TRUE), 1)
CT.50p.mean                 <- format(mean(catch50prop.spring$meanDate50p[catch50prop.spring$Species=="CT"], na.rm = TRUE), "%B %d")
CT.50p.SD                   <- round(sd(catch50prop.spring$Date50pDiff[catch50prop.spring$Species=="CT"], na.rm = TRUE), 1)
CT.peak.mean                <- format(mean(catch_peak.spring$date.std_CT,na.rm = TRUE), "%B %d")
CT.peak.SD                  <- round(sd(catch_peak.spring$MeanDiff_CT,na.rm = TRUE),1)


CO.first.detection.earliest <- format(min(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"]), "%B %d")
CO.first.detection.latest   <- format(max(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"]), "%B %d")
CO.first.detection.mean     <- format(mean(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"], na.rm = TRUE), "%B %d")
CO.first.detection.SD       <- round(sd(pass.period.spring$minMeanDiff[pass.period.spring$Species=="CO"], na.rm = TRUE), 1)
CO.50p.mean                 <- format(mean(catch50prop.spring$meanDate50p[catch50prop.spring$Species=="CO"], na.rm = TRUE), "%B %d")
CO.50p.SD                   <- round(sd(catch50prop.spring$Date50pDiff[catch50prop.spring$Species=="CO"], na.rm = TRUE), 1)
CO.peak.mean                <- format(mean(catch_peak.spring$date.std_CO,na.rm = TRUE), "%B %d")
CO.peak.SD                  <- round(sd(catch_peak.spring$MeanDiff_CO,na.rm = TRUE),1)

```

Outmigrating juvenile CCT and Coho Salmon were first encountered at the trap over a similar period, from `r CT.first.detection.earliest` to `r CT.first.detection.latest` (mean $\pm$ SD = `r CT.first.detection.mean` $\pm$ `r CT.first.detection.SD` days) for CCT and `r CO.first.detection.earliest` to `r CO.first.detection.latest` for Coho (mean $\pm$ SD = `r CO.first.detection.mean` $\pm$ `r CO.first.detection.SD` days). On average 50% of all CCT had passed the fence by `r CT.50p.mean`$\pm$ `r CT.50p.SD` days while half of Coho Salmon migrants had passed the fence by `r CO.50p.mean`$\pm$ `r CO.50p.SD` days. Despite similarities in when migrations started and the timing that most migrants had past the fence, there was a noticeable difference in the timing of peak migrations (the date when the greatest number of fish passed the fence). For Coastal CCT, the overall mean $\pm$ SD peak migration occurred on `r CT.peak.mean`($\pm$ `r CT.peak.SD` days) (Figure 5) whereas overall mean peak Coho Salmon migration occurred more than a week later on `r CO.peak.mean` ($\pm$ `r CO.peak.SD` days) (Figure 6). Total number of daily captures of CCT and Coho Salmon per year are presented in Figure 6 and Figure 7, respectively. 

#### Migration Timing Tables and Figures

#### Figure 4. Overall Capture Timing
```{r 5. Capture Timing - Overall Median Capture Timing, fig.cap = "Figure 4. Overall median spring capture timing.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 6}
Spring.Boxplot.Summary
```


#### Figure 5. Median Spring CO Capture Timing Across Years
```{r 5. Capture Timing - Median Spring CO Capture Timing, fig.cap = "Figure 5. Median spring cpature timing", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12}
Spring.Boxplot.Years.CO
```

#### Figure 6. Median Spring CT Capture Timing Across Years
```{r 5. Capture Timing - Median Spring CCT Capture Timing, fig.cap = "Figure 6. Median spring cpature timing", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12}
Spring.Boxplot.Years.CO
```

#### Figure 7. Frequency of Peak CCT Migration
```{r 5. Capture Timing - Frequency of Peak CT Capture, fig.cap = "Figure 7. Frequency of peak CCT capture dates during Spring fence monitoring.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12 }
print(CT.peak.spring.plot)
```

#### Figure 8. Daily captures of CCT per year
```{r 5. Capture Timing - Daily CT Captures per year, fig.cap = "Figure 8. Total daily capture of CCT and proportion of total annual captures.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Spring.CT)
```

#### Figure 9. Total daily captures of CCT across years
```{r 5. Capture Timing - Daily CT Captures Across Years, fig.cap = "Figure 9. Total daily capture of CCT across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 10}

print(daily_catch_summary_plot.Spring.CT)
```


#### Figure 10. Frequency of Peak Coho Migration
```{r 5. Capture Timing - Frequency of Peak CO Capture, fig.cap = "Figure 10. Frequency of peak Coho capture dates during Spring fence monitoring.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12 }

print(CO.peak.spring.plot)

```

#### Figure 11. Total daily captures of Coho Salmon per year
```{r 5. Capture Timing - Daily CO Captures per year, fig.cap = "Figure 11. Number of Coho Salmon captured during each day of spring fence operation since 2008.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Spring.CO)
```

####  Figure 12. Total daily captures of Coho across years
```{r 5. Capture Timing - Daily CO  Captures Across Years, fig.cap = "Figure 12. Total daily capture of CCT across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 8}

print(daily_catch_summary_plot.Spring.CO)
```

### 2.5 Length Frequency {.tabset .tabset-dropdown}
```{r 6. Length Frequency - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/6. Length Frequency.R")
```

```{r 6. length values, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
spring.dat <- data_all %>% filter(Period == "Spring",
                                  Length>20,
                                  Species %in% c("CO","CT"))
CO_min <- min(spring.dat$Length[spring.dat$Species=="CO"], na.rm = TRUE)
CO_max <- max(spring.dat$Length[spring.dat$Species=="CO"], na.rm = TRUE)


CT_min <- min(spring.dat$Length[spring.dat$Species=="CT"], na.rm = TRUE)
CT_max <- max(spring.dat$Length[spring.dat$Species=="CT"], na.rm = TRUE)

Aged <- spring.dat %>% mutate(Age =ifelse(Species == "CO",
                                          ifelse(Length <110, 0, 1),
                                    ifelse(Species == "CT", 
                                         ifelse(Length <80, 0,
                                               ifelse(Length <150, 1, 2)),NA))) %>%
                        select(Period, Species, Length, Age)

                          
    age.table <- Aged %>% mutate(Age = as.factor(Age)) %>%
                          group_by(Species, Age) %>%
                          summarise(n = n(),
                                    min = min(Length),
                                    max = max(Length),
                                    avg = mean(Length))
    
CO.Age0.perc <- age.table$n[age.table$Species =="CO" & age.table$Age ==0]/(age.table$n[age.table$Species =="CO" & age.table$Age ==0]+
                                                                          age.table$n[age.table$Species =="CO" & age.table$Age ==1])
                                                                       
```


#### Length Frequency Table and Figures
The length frequency figures shown below shed light on the population structure and behaviours of Coho Salmon and CCT in Simms Creek. The lengths of CCT (`r CT_min` mm to `r CO_max` mm) and Coho Salmon (`r CO_min` mm to `r CO_max` mm) measured at the fence suggest multiple age classes of juveniles are moving out of the system each spring. Assuming that CO <100 mm are Age 0 and CO >100 mm are Age 1 would suggest that `r percent(round(CO.Age0.perc,digits = 3))` of all overall migrants are Age 0 and the remainder are Age 1. A wider range of age classes is likely present among CCT, including Age 0 fish (~<80 mm) up to mature fish > 230 mm and upwards of 3+ years. 

Mature CCT >230 mm represent <`r percent(round(CT.AgeClass.Prop$Adult, digits =3))` of the total catch of CCT. However, all mature CCT >230 mm were moving downstream, suggesting that they either 1) moved upstream and spawned prior to the start of fence operation or 2) had overwintered in Simms Creek and were follow fry out in the spring - whether this was their first movement to the ocean is unknown. 



#### Figure 13. Length Frequency of all CCT
```{r Length Frequency - CT Length Frequency All Years Combined, fig.cap = "Figure 13. Length Frequency of all CCT.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 8, fig.height = 6}

print(LF.plot_spring.all.CT)
```


#### Figure 14. Length frequency of Coastal CCT across years.
```{r 6. Length Frequency - CT Length Frequency Across Years, fig.cap = "Figure 14. Length Frequency of CCT across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

print(LF.plot_spring.CT)
```

#### Figure 15. Length frequency of all Coho Salmon.
```{r 6. Length Frequency - CO Length Frequency All Years Combined, fig.cap = "Figure 15. Length Frequency of All Coho Salmon.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 8, fig.height = 6}

print(LF.plot_spring.all.CO)
```

#### Figure 16. Length frequency of Coho Salmon across years.
```{r 6. Length Frequency - CO Length Frequency Across Years, fig.cap = "Figure 16. Length Frequency of CCT across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

print(LF.plot_spring.CO)
```



## 2.6 What are these fish doing???
```{r 8. Spring Spawners - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/8. SpringSpawners.R")
```

CCT show incredible diversity in the timing of their life history behaviours. Throughout their range, spawning has been documented in nearly every month of the year. In Puget Sound for instance, spawning has been reported from November through March and timing is highly variable between years ([Losee et al. 2016](https://afspubs.onlinelibrary.wiley.com/doi/abs/10.1080/02755947.2015.1129001#:~:text=These%20types%20of%20data%20have%20suggested%20a,coastal%20stream%20of%20southern%20Puget%20Sound%2C%20Washington.)). The spawn timing of CCT in Simms Creek is unknown, or at least undocumented, however, I Would assume it occurs during a similar period to Puget Sound and is equally variable. 

The current dataset does provide some insight on spawn timing. Presumably, spawners will be >150 mm in length. 

##--------------------------

```{r exit}
knitr::knit_exit()
```

##--------------------------

```{r CCT - cum.Catch.plot,echo=FALSE, warning=FALSE, message = FALSE, fig.width = 9, fig.height = 15}

labels <- data.frame(Year = unique(Spring.Catch$Year), YYYEAR = unique(Spring.Catch$Year)) %>%
          # data.frame(Year = unique(CCT_catch$Year), YYYEAR = unique(CCT_catch$Year)) %>%
          mutate(YYYEAR = ifelse(Year == 2020, "2020 - COVID",
                                 ifelse(Year == 2021,"2021 - COVID",
                                        ifelse(Year == 2023, "2023 - Strike",Year))),
                 labX = as.Date(ifelse(Year == 2020, as.Date("2024-05-25"),
                                 ifelse(Year == 2021,as.Date("2024-05-25"),
                                        ifelse(Year == 2023, as.Date("2024-05-25"),as.Date("2024-04-16"))))))
ggplot(Spring.Catch) + 
      geom_col(aes(x= date.std, y =catch))+
      geom_line(aes(x= date.std, y = prop.scaled)) +
      geom_label(data = labels, aes(label = YYYEAR),
                x = as.Date("2024-04-15"), y = 205,
                hjust = "left", vjust = 0,
                inherit.aes = FALSE)+
      scale_x_date(date_breaks = "2 week", date_labels = "%b-%d") +
      scale_y_continuous("Total Captures (# of Fish)",
                         sec.axis = sec_axis(~./300, 
                         name = "Proportion of Total Catch (%)"))+
      facet_grid(Year~Species) +
      labs(x="", y = "Total Captures (# of Fish)") +
      theme_bw() +
      theme(strip.text.y = element_blank())
    
```

```{r CCT - cum.Catch.plot2,echo=FALSE, warning=FALSE, message = FALSE }
    ggplot(CCT_catch) +
        geom_line(aes(x= date.std, y = prop, color = Year)) +
        labs(x = "", y = "Proportion of Total Catch (%)") +
        scale_x_date(date_breaks = "1 week", 
                     minor_breaks = "1 day",
                     date_labels = '%b-%d')+ 
        facet_grid(Decade~.)+
        theme_bw() +
        theme(legend.position = "bottom")



```

```{r CT Catch Summary, echo=FALSE, warning=FALSE, message = FALSE}
### Prep Data ----
CT_catch <- catch_summary %>%
            select(1:13) %>%  # Select CT Data
            pivot_wider(names_from = Period, values_from = 3:13) %>%
            select(1, ends_with("Spring"), ends_with("Fall")) %>%
            ungroup() %>%
            add_row(Year = c(2020, 2021, 2023)) %>%
            arrange(Year)


## CT Kable ----
kable(CT_catch,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Year","Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max",
                    "Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 1. Spring and Fall Trapping of CCT.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" "=1, "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4,
                     "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4)) %>%
  add_header_above(c(" " = 1,"Spring" = 11, "Fall" = 11)) 
 
```

```{r CT Size Distribution, length-frequency all years,echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of all CCT captured to date.
    ## Prepare Data
    CT_dat <- data_all %>% 
                    filter(Species == "CT") %>%
                    mutate(date.std =  case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
                    

      ## Prepare Plot
      all_years.plot <- ggplot(CT_dat) +
                            geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                            labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                            scale_x_continuous(breaks = seq(50, 450, by = 25))+
                            #scale_y_continuous(breaks = seq(0, 450, 50))+
                            theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                            theme_bw() +
                            facet_grid(Year~.)
```

```{r compare regional trends, echo=FALSE, warning=FALSE, message = FALSE}
## Prep Regional Abundance Dataset
reg.abund <- reg.dat %>% 
                mutate(data_set = "DFO") %>%
                select(data_set, year, species, spawners, smoothedSpawners) %>%
                rename(Year     = year,
                       Species  = species,
                       n        = spawners,
                       n_smooth = smoothedSpawners) %>% 
                mutate(Species = recode(as.factor(Species),
                                                 "Coho"      = "CO_Adult",
                                                 "Chinook"   = "CN",
                                                 "Pink"      = "PK",
                                                 "Chum"      = "CM",
                                                 "Sockeye"   = "SK",
                                                 "Steelhead" = "ST"),
                                Species = factor(Species, 
                                                 levels = c("CT","CO_Adult", "CN","CM","PK", "SK", "ST")))
# Prepare Simms Data and Join with Regional Data                
catch_spring <- data_all %>%
                    filter(Period == "Spring",
                           Species %in% c("CT", "CO")) %>%
                    group_by(Year,Species) %>%
                    summarise(n = n()) %>%
                    filter(!is.na(Species)) %>%
                    mutate(n_smooth = 0,
                           data_set = "Simms") %>% 
                    relocate(data_set) %>%
                rbind(reg.abund)

catch_spring_CO <- catch_spring %>%
                      filter(Year >= 2008) %>%
                      select(!n_smooth)

ggplot(catch_spring_CO, 
       aes(x = Year, y = n)) +
  geom_point() + 
  geom_line() + 
  facet_grid(Species ~., scales = "free")

catch_spring_long <- catch_spring_CO %>%
      select(!data_set) %>%
      pivot_wider(names_from = Species, values_from = n) %>%
      drop_na()

cor(catch_spring_long)
```

# 3. Fall Fence Operation
### 3.1. Monitoring Effort

Fall surveys to count the number returning adult Coho, Chinook, Chum and Pink Salmon and also intercept a small number of CCT. In the fall, surveys have started as early as `r format(min(trap_plot$date.std[trap_plot$Period=="Fall"]), "%B %d")`, however, most surveys (50%) have started on `r format(min(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled >= 0.5]), "%B %d")`. In each monitoring year, surveys have occurred continuously (e.g., sampling occurred daily) from `r format(min(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled == 1.0]), "%B %d")` to `r format(max(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled == 1.0]), "%B %d")`. Surveys have continued as late as `r format(max(trap_plot$date.std[trap_plot$Period =="Fall"]), "%B %d")` and no surveys have occurred later than `r format(max(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled >= 0.5]), "%B %d")`.

## 3.2. Stream Conditions
During each trap daily trap visit, volunteers record measures of water temperature, pH, Total Suspended Sediment (TSS), dissolved oxygen, and water level (stage). Mean annual measures of each parameter are presented below for the Fall monitoring period (Table 2 and Figure 3).

```{r 3. Stream Conditions - Fall Table, fig.cap = "Table 3. Overall annual stream conditions during fall trap monitoring from 2008 to 2024.", fig.topcaption = TRUE,echo=FALSE, warning=FALSE, message = FALSE}

cond_data_wide.fall <- cond_data_wide %>% select(1,14:25)

## Kable - Stream Conditions ----
options(knitr.kable.NA = '-')
    

    kable(cond_data_wide.fall,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c(" ", "Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD"),
      caption = "Table 3. Stream conditions during fall trap operation.",
      
      digits = 1) %>%
  column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>% 
  add_header_above(c(" " = 1, "Air Temp. \n(\u00B0C)" = 2, "Water Temp. \n(\u00B0C)" = 2, 
                              "pH \n. " = 2, "DO \n(mg/L)" = 2, "TDS \n(ppm)" = 2, "Water Level \n(m)" = 2)) %>%
  add_header_above(c("Year"= 1, "Fall Monitoring" = 12))    



```


```{r 2. Trap Effort - Spring Plot, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 15, fig.height = 5, fig.cap = "Figure 1. Spring juvenile trap operation effort, presented as the proportion of sample years when trapping was completed on each date.", fig.topcaption = TRUE}

print(trap_effort_plot_spring)

```
