---
title: "SimmsFishFence"
author: "Eric V"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
    highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
    fig_caption: true
    code_folder: show
    smart: true
    toc: true
    toc_float: 
      toc_depth: 1
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll 
  html_notebook:
    toc: yes  


#bibliography: biobliography.bib
    
---

```{r old yaml, include = FALSE}


# <!--   flexdashboard::flex_dashboard: -->
# <!--     orientation: columns -->
# <!--     vertical_layout: scroll -->
# <!--   html_notebook: -->
# <!--     toc: true -->
# <!--   word_document: -->
# <!--     toc: true -->
# <!-- editor_options: -->
# <!--   chunk_output_type: inline -->
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

# 1. Introduction

Simms Creek is a small, 3rd order stream that drains an area of \~1,800 ha into the Salish Sea, near Campbell River's Willow Point neighborhood. The lower reach of Simms Creek (\~3 km of channel, east of Dogwood Street), is contained within a narrow urban green way that is bordered by residential properties. From Dogwood Street Road the streams runs for ~ 2 km to the Inland Highway and is protected within [Beaver Lodge Lands](https://campbellriver.travel/news/forestry-guide-to-beaver-lodge-lands/), upstream of the Inland Highway, \>1.5 km of tributary channel is located within private forest lands in various stages of regeneration.

Chum, Chinook, Pink and Coho salmon have all been observed in Simms Creek, as well as Coastal Cutthroat Trout (CCT), Rainbow Trout and steelhead. More recent monitoring (i.e., this dataset), suggest that Coho Salmon (CO) and CCT are the primary species within Simms Creek, both of which are present within the stream year round - though a small number of juvenile Chinook Salmon were identified in 2024.

[Greenways Land Trust](https://www.greenwaystrust.ca/) has supported Simms Creek Stewards for +20 years, including operation of a fish fence near the mouth of the stream since 2008. Juvenile and adult fish moving past the fence are tallied each spring and fall, respectively. The objective of this project is to explore the juvenile fence dataset. All work is being done strictly for fun and out of personal curiosity. Any feedback, input, or support is welcome. Also, I have a soft spot for CCT, so be warned that effort and results will be slightly trout biased. Let's take a look at what has been completed to date. It's a tremendous amount of work and all volunteers and supporters should be commended!



```{r 1. Load and Format Data, echo = FALSE, warning = FALSE, message = FALSE}
## Clear workspace ##
# rm(list = ls())  

# ## Load Prepped Data
# source("SourceFiles/0. RunSourceFiles.R")
# 
  source("SourceFiles/1. Load and Prep Data.R")
# 
# ## Load Trap Effort Data
 source("SourceFiles/2. Trapping Effort.R")

```

```{r download data}
data_all %>%
download_this(
    output_name = "Raw Fence Data",
    output_extension = ".csv",
    button_label = "Download Fence Data (.csv)",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

simms_env %>%
download_this(
    output_name = "Raw Fence Data",
    output_extension = ".csv",
    button_label = "Download Enviromental Data (.csv)",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```


# 2. Fence Operation

### 2.1. Monitoring Effort {.tabset .tabset-dropdown}
The Simms Creek fish fence has operated annually since 2008, with the exception of 2020 and 2021 when operations were paused due to the COVID-19 Pandemic and in the spring of 2023 when federal employees were on strike.

Spring surveys target out migrating juvenile Coho Salmon but also capture an impressive number of CCT and have even captured some Chinook Salmon. Spring fence monitoring has started as early as `r format(min(trap_plot$date.std[trap_plot$Period=="Spring"]), "%B %d")`, however, most surveys (50%) don't start until `r format(min(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled >= 0.5]), "%B %d")`. In each monitoring year, the fence has operated continuously (e.g., sampling occurred at least daily) from `r format(min(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled == 1.0]), "%B %d")` to `r format(max(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled == 1.0]), "%B %d")`. Surveys have continued as late as `r format(max(trap_plot$date.std[trap_plot$Period=="Spring"]), "%B %d")`, but most (50%) are terminated by `r format(max(trap_plot$date.std[trap_plot$Period=="Spring" & trap_plot$prop.sampled==0.5]), "%B %d")`.

Fall surveys to count the number returning adult Coho, Chinook, Chum and Pink Salmon and also intercept a small number of CCT. In the fall, surveys have started as early as `r format(min(trap_plot$date.std[trap_plot$Period=="Fall"]), "%B %d")`, however, most surveys (50%) have started on `r format(min(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled >= 0.5]), "%B %d")`. In each monitoring year, surveys have occurred continuously (e.g., sampling occurred daily) from `r format(min(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled == 1.0]), "%B %d")` to `r format(max(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled == 1.0]), "%B %d")`. Surveys have continued as late as `r format(max(trap_plot$date.std[trap_plot$Period =="Fall"]), "%B %d")` and no surveys have occurred later than `r format(max(trap_plot$date.std[trap_plot$Period=="Fall" & trap_plot$prop.sampled >= 0.5]), "%B %d")`.


#### Monitoring Effort Tables and Figures

#### Table 1. Sampling Summary
```{r 2. Trap Effort Summary Table , fig.cap = "Table 1. Summary of spring and fall sampling effort.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE}

kable(trap_effort_summary_table,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c("Period","Min","Max", "Mean", "SD",
                             "Min","Max", "Mean", "SD",
                             "Min","Max", "Mean", "SD"),
      caption = "Table 1. Annual spring trap operation periods.",
      digits = 1) %>%
    
      kable_styling("striped", full_width =  FALSE,
                      position = "center", 
                      font_size = 12,
                      fixed_thead = TRUE) %>%
        add_header_above(c(" " = 1, "# Days Sampled" = 4, "Start Date" = 4, "End Date"=4))

```


#### Table 2. Annual Spring and Fall Trap Operation Periods
```{r 2. Trap Effort Table trap effort table, fig.cap = "Table 2. Annual spring and fall trap operation periods.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE}


## Kable - Master Summary ----
options(knitr.kable.NA = '-')
    

    kable(trap_effort_table,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c("Year", "# Days Sampled", "Start", "End", 
                            "# Days Sampled", "Start", "End"),
      caption = "Table 2. Annual spring and fall trap operation periods.",
      
      digits = 1) %>%
  column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" " = 1, "Spring Sampling" = 3, "Fall Sampling" = 3))
```


<!-- **`r fig_nums("fall.trap.plot", "Fall trap operation period, presented as the proportion of sample years each date has been trapped since 2008 (excluding years when trapping did not occur due to COVID or government strikes).")`** -->



```{r 3. Stream Conditions - Load Data, echo=FALSE, warning=FALSE, message = FALSE}

## Load Stream Conditions Data 
 source("SourceFiles/3. Stream Conditions.R")

```

### 2.2 Stream Conditions {.tabset .tabset-dropdown}

During each daily trap visit, volunteers record measures of water temperature, pH, Total Suspended Sediment (TSS), dissolved oxygen, and water level (stage). Mean annual measures of each parameter are presented below for the spring and fall monitoring periods (Table 3 and Table 4, Figure 2). 

#### Stream Conditions Figures and Tables

#### Table 3. Spring Condition Table
```{r 3. Stream Conditions - Spring Table, fig.cap = "Table 3. Overall annual stream conditions during spring trap monitoring from 2008 to 2024.", fig.topcaption = TRUE,echo=FALSE, warning=FALSE, message = FALSE}

cond_data_wide.spring <- cond_data_wide %>% select(1:13)

## Kable - Stream Conditions ----
options(knitr.kable.NA = '-')
    

    kable(cond_data_wide.spring,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c(" ", "Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD"),
      caption = "Table 3. Stream conditions during spring trap operation.",
      
      digits = 1) %>%
  column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>% 
  add_header_above(c(" " = 1, "Air Temp. \n(\u00B0C)" = 2, "Water Temp. \n(\u00B0C)" = 2, 
                              "pH \n. " = 2, "DO \n(mg/L)" = 2, "TDS \n(ppm)" = 2, "Water Level \n(m)" = 2)) %>%
  add_header_above(c("Year"= 1, "Spring Monitoring" = 12))    

```

#### Table 4. Fall Condition Table
```{r 3. Stream Conditions - Fall Table, fig.cap = "Table 4. Overall annual stream conditions during fall trap monitoring from 2008 to 2024.", fig.topcaption = TRUE,echo=FALSE, warning=FALSE, message = FALSE}

cond_data_wide.spring <- cond_data_wide %>% select(1, 14:25)

## Kable - Stream Conditions ----
options(knitr.kable.NA = '-')
    

    kable(cond_data_wide.spring,
      "html",
      booktabs = T,
      
      align = c("c"),
      col.names = c(" ", "Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD","Mean","SD"),
      caption = "Table 4. Stream conditions during fall trap operation.",
      
      digits = 1) %>%
  column_spec(c(2,5), width = "2cm") %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>% 
  add_header_above(c(" " = 1, "Air Temp. \n(\u00B0C)" = 2, "Water Temp. \n(\u00B0C)" = 2, 
                              "pH \n. " = 2, "DO \n(mg/L)" = 2, "TDS \n(ppm)" = 2, "Water Level \n(m)" = 2)) %>%
  add_header_above(c("Year"= 1, "Fall Monitoring" = 12))    
```



#### Figure 2. Spring and Fall Condition Plot
```{r 3. Stream Conditions - Plot, fig.cap = "Figure 2. Average daily measures of air and water temperature, pH, dissolved oxygen (DO), total dissolved solids (TDS) and water level (stage) per monitoring year in spring and fall.", echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 15, fig.topcaption = TRUE}

print(cond_plot)
```

### 2.3. Annual Captures {.tabset .tabset-dropdown}
```{r 4. Fish Captures - Summary Table catch_dat.prep, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
source("SourceFiles/4. Annual Captures.R")
```

```{r 4. Fish Captures - values for text, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
annual.catches <- catch_plot.data %>% group_by(Period, Species) %>%
                                         summarize(mean = round(mean(n),0),
                                                   min = min(n),
                                                   max = max(n),
                                                   SD  = sd(n))
annual.catches.spring.CT <- annual.catches %>% filter(Period == "Spring", Species == "CT")
annual.catches.spring.CO <- annual.catches %>% filter(Period == "Spring", Species == "CO")
annual.catches.fall.CT <- annual.catches %>% filter(Period == "Fall", Species == "CT")
annual.catches.fall.CO <- annual.catches %>% filter(Period == "Fall", Species == "CO")
```



Since 2008, a total of `r format(sum(catch_annual.Table.Spring$nCT), big.mark =",")` juvenile CCT and `r format(sum(catch_annual.Table.Spring$nCO), big.mark =",")` juvenile Coho Salmon have been captured during spring trapping. Annual captures of CCT have ranged from `r format(min(catch_annual.Table.Spring$nCT), big.mark =",")` to `r format(max(catch_annual.Table.Spring$nCT), big.mark =",")` (mean = `r format(mean(catch_annual.Table.Spring$nCT), digits = 1)`) while CO captures have varied from `r format(min(catch_annual.Table.Spring$nCO), big.mark =",")` to `r format(max(catch_annual.Table.Spring$nCO), big.mark =",")` with an overall mean of `r format(mean(catch_annual.Table.Spring$nCO), digits = 1)` fish (Figure 3 and Figure 4, Table 5 and Table 6).

As expected, most fish are captured in the Spring. Catches of CCT have ranged from `r annual.catches.spring.CT$min` to `r annual.catches.spring.CT$max` during spring (mean = `r annual.catches.spring.CT$mean` $\pm$ `r round(annual.catches.spring.CT$SD,1)`) compared to only `r annual.catches.fall.CT$min` to `r annual.catches.fall.CT$max` fish during fall (mean = `r annual.catches.fall.CT$mean` $\pm$ `r round(annual.catches.fall.CT$SD,1)`). 


#### Annual Captures Figures and Tables

#### Figure 3. Spring - Total annual catches
```{r 4. Annual Captures - Spring Summary Plot, fig.cap = "Figure 3. Total annual catch of CCT and Coho Salmon during Spring fence monitoring.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12}

print(catch_annual_barPlot.Spring)
```
#### Table 5. Spring - Total annual catches
```{r 4. Annual Captures - Spring Summary Table, echo=FALSE, warning=FALSE, message = FALSE}
## Kable - Master Summary ----
options(knitr.kable.NA = '-')

catch_annual.Table.Spring %>% group_by(Year) %>% mutate(total.catch = nCT + nCO)

kable(catch_annual.Table.Spring  %>% group_by(Year) %>% mutate(total.catch = nCT + nCO),
      "html",
      booktabs = T,
      
      align = c("c"),
      # col.names = c("Year", "Period", "Start", "End", "# Days Sampled", 
      col.names = c("Year", "Start", "End", "# Days Sampled",  
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max",
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max", "n"),
      caption = "**Table 5. Spring capture summary - capture timing, total captures and length of CCT and Coho Salmon.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  # add_header_above(c(" " = 2, "Sample Period" = 3, 
  add_header_above(c(" " = 1, "Sample Period" = 3,                   
                     "Capture Timing" = 3,"Fork Length (mm)" = 5,
                     "Capture Timing" = 3,"Fork Length (mm)" = 5,"(CT+CO)"=1)) %>%
  add_header_above(c(" " = 4, "CCT" = 8, "Coho Salmon" = 8,"Total"=1)) 
```

#### Figure 4. Fall - Total annual catches
```{r 4. Annual Captures - Fall Summary Plot, fig.cap = "Figure 4. Total annual catch of CCT and Coho Salmon during fall fence monitoring.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 12}

print(catch_annual_barPlot.Fall)
```

#### Table 6. Fall - Total annual catches
```{r Annual Captures - Fall Summary Table, echo=FALSE, warning=FALSE, message = FALSE}
## Kable - Master Summary ----
options(knitr.kable.NA = '-')

kable(catch_annual.Table.Fall,
      "html",
      booktabs = T,
      
      align = c("c"),
      # col.names = c("Year", "Period", "Start", "End", "# Days Sampled", 
      col.names = c("Year", "Start", "End", "# Days Sampled",  
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max",
                    "Med.","Min","Max", "n", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 6. Fall capture summary - capture timing, total captures and length of CCT and Coho Salmon.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  # add_header_above(c(" " = 2, "Sample Period" = 3, 
  add_header_above(c(" " = 1, "Sample Period" = 3,                   
                     "Capture Timing" = 3,"Fork Length (mm)" = 5,
                     "Capture Timing" = 3,"Fork Length (mm)" = 5)) %>%
  add_header_above(c(" " = 4, "CCT" = 8, "Coho Salmon" = 8)) 
```
### 2.4 Length Frequency {.tabset .tabset-dropdown}
```{r 6. Length Frequency - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/6. Length Frequency.R")
```

```{r 6. length values, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
spring.dat <- data_all %>% filter(Period == "Spring",
                                  Length>20,
                                  Species %in% c("CO","CT"))
CO_min <- min(spring.dat$Length[spring.dat$Species=="CO"], na.rm = TRUE)
CO_max <- max(spring.dat$Length[spring.dat$Species=="CO"], na.rm = TRUE)


CT_min <- min(spring.dat$Length[spring.dat$Species=="CT"], na.rm = TRUE)
CT_max <- max(spring.dat$Length[spring.dat$Species=="CT"], na.rm = TRUE)

Aged <- spring.dat %>% mutate(Age =ifelse(Species == "CO",
                                          ifelse(Length <110, 0, 1),
                                    ifelse(Species == "CT", 
                                         ifelse(Length <80, 0,
                                               ifelse(Length <150, 1, 2)),NA))) %>%
                        select(Period, Species, Length, Age)

                          
    age.table <- Aged %>% mutate(Age = as.factor(Age)) %>%
                          group_by(Species, Age) %>%
                          summarise(n = n(),
                                    min = min(Length),
                                    max = max(Length),
                                    avg = mean(Length))
    
CO.Age0.perc <- age.table$n[age.table$Species =="CO" & 
                            age.table$Age ==0]/(age.table$n[age.table$Species =="CO" & 
                                                           age.table$Age ==0]+ 
                                                  age.table$n[age.table$Species =="CO" & 
                                                            age.table$Age ==1])
                                                                       
```


The length frequency figures shown below shed light on the population structure and behaviours of Coho Salmon and CCT in Simms Creek. The lengths of CCT (`r CT_min` mm to `r CO_max` mm) and Coho Salmon (`r CO_min` mm to `r CO_max` mm) measured at the fence suggest multiple age classes of juveniles are moving out of the system each spring. Assuming that CO <100 mm are Age 0 and CO >100 mm are Age 1 would suggest that `r percent(round(CO.Age0.perc,digits = 3))` of all overall migrants are Age 0 and the remainder are Age 1. A wider range of age classes is likely present among CCT, including Age 0 fish (~<80 mm) up to mature fish > 230 mm and upwards of 3+ years. 

Mature CCT >230 mm represent <`r percent(round(CT.AgeClass.Prop$Adult, digits =3))` of the total catch of CCT. However, all mature CCT >230 mm were moving downstream, suggesting that they either 1) moved upstream and spawned prior to the start of fence operation or 2) had overwintered in Simms Creek and were follow fry out in the spring - whether this was their first movement to the ocean is unknown. 

#### Length Frequency Table and Figures

#### Figure 5. Length Frequency of all CCT
```{r 6. Length Frequency - CT Length Frequency All Years Combined, fig.cap = "Figure 5. Length Frequency of all CCT.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 8, fig.height = 6}

print(LF.plot_spring.all.CT)
```


#### Figure 6. Length frequency of Coastal CCT across years.
```{r 6. Length Frequency - CT Length Frequency Across Years, fig.cap = "Figure 6. Length Frequency of CCT across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

print(LF.plot_spring.CT)
```

#### Figure 7. Length frequency of all Coho Salmon.
```{r 6. Length Frequency - CO Length Frequency All Years Combined, fig.cap = "Figure 7. Length Frequency of All Coho Salmon.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 8, fig.height = 6}

print(LF.plot_spring.all.CO)
```

#### Figure 8. Length frequency of Coho Salmon across years.
```{r 6. Length Frequency - CO Length Frequency Across Years, fig.cap = "Figure 8. Length Frequency of Coho Salmon across years.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

print(LF.plot_spring.CO)
```

### 2.5 Age Composition
```{r 10. AgeClasses - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
source("SourceFiles/10. AgeClasses.R")
```

No scale data has been collected during juvenile enumeration work on Simms Creek. However, information collected on systems within the region suggests we can loosely apply the following age classes to juvenile CT and CO:

  -  CT < 80  ~ Age-0 
  -  CT < 120 ~ Age-1
  -  CT < 200 ~ Age-2
  -  CT > 200 ~ Age-2+
  -  CO < 80  ~ Age-0
  -  CO < 120 ~ Age-1
  -  CO > 120 ~ Age-1+ 

Applying these age bins to the length frequency data suggests that CCT are range in age from Age-1 to Age 3+, but are primarily Age-2 (Figure 9), while CO are almost exclusively Age-1 (Figure 10). Interestingly, Age-0 CO were present in 2009 and 2024, but not other years. While this may be coincidental, it's worth noting that the peak juvenile CCT counts were recorded in 2008 and 2024. There are a number of mechanisms that may explain why Age-0 CO were first observed in 2024: 1) they weren't recorded in past years, CO emigrated out of Simms Creek earlier than normal due to high CT abundance.

#### Figure 9. Age composition across years.
```{r 10. Age Class - CT Age Class Composition across years, fig.cap = "Figure 9. Assumed age class composition of juvenile CCT and Coho Salmon out migrating from Simms Creek since 2008.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

juv.AgeClass.plot

```


#### Figure 10. Size by age class across years.
```{r 10. Age Class - Age Class Size across years, fig.cap = "Figure 10. Median size by age class of fish outmigrating from Simms Creek since 2008.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 20}

age.class.size

```

### 2.6. Migration Timing {.tabset .tabset-dropdown}
```{r 5. Capture Timing - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/5. Capture Timing.R")
```

```{r 5. Capture Timing - Prepare spring text values, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE }

## Spring data for text
CT.first.detection.earliest <- format(min(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"]), "%B %d")
CT.first.detection.latest   <- format(max(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"]), "%B %d")
CT.first.detection.mean     <- format(mean(pass.period.spring$minPass.min[pass.period.spring$Species=="CT"], na.rm = TRUE), "%B %d")
CT.first.detection.SD       <- round(sd(pass.period.spring$minMeanDiff[pass.period.spring$Species=="CT"], na.rm = TRUE), 1)
CT.50p.mean                 <- format(mean(catch50prop.spring$meanDate50p[catch50prop.spring$Species=="CT"], na.rm = TRUE), "%B %d")
CT.50p.SD                   <- round(sd(catch50prop.spring$Date50pDiff[catch50prop.spring$Species=="CT"], na.rm = TRUE), 1)
CT.peak.mean                <- format(mean(catch_peak.spring$date.std_CT,na.rm = TRUE), "%B %d")
CT.peak.SD                  <- round(sd(catch_peak.spring$MeanDiff_CT,na.rm = TRUE),1)


CO.first.detection.earliest <- format(min(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"]), "%B %d")
CO.first.detection.latest   <- format(max(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"]), "%B %d")
CO.first.detection.mean     <- format(mean(pass.period.spring$minPass.min[pass.period.spring$Species=="CO"], na.rm = TRUE), "%B %d")
CO.first.detection.SD       <- round(sd(pass.period.spring$minMeanDiff[pass.period.spring$Species=="CO"], na.rm = TRUE), 1)
CO.50p.mean                 <- format(mean(catch50prop.spring$meanDate50p[catch50prop.spring$Species=="CO"], na.rm = TRUE), "%B %d")
CO.50p.SD                   <- round(sd(catch50prop.spring$Date50pDiff[catch50prop.spring$Species=="CO"], na.rm = TRUE), 1)
CO.peak.mean                <- format(mean(catch_peak.spring$date.std_CO,na.rm = TRUE), "%B %d")
CO.peak.SD                  <- round(sd(catch_peak.spring$MeanDiff_CO,na.rm = TRUE),1)

```

**2.4.1 Spring Outmigration**

Outmigrating juvenile CCT and Coho Salmon were first encountered at the trap over a similar period, from `r CT.first.detection.earliest` to `r CT.first.detection.latest` (mean $\pm$ SD = `r CT.first.detection.mean` $\pm$ `r CT.first.detection.SD` days) for CCT and `r CO.first.detection.earliest` to `r CO.first.detection.latest` for Coho (mean $\pm$ SD = `r CO.first.detection.mean` $\pm$ `r CO.first.detection.SD` days). On average 50% of all CCT had passed the fence by `r CT.50p.mean`$\pm$ `r CT.50p.SD` days while half of Coho Salmon migrants had passed the fence by `r CO.50p.mean`$\pm$ `r CO.50p.SD` days. Despite similarities in when migrations started and the timing that most migrants had past the fence, there was a noticeable difference in the timing of peak migrations (the date when the greatest number of fish passed the fence). For Coastal CCT, the overall mean $\pm$ SD peak migration occurred on `r CT.peak.mean`($\pm$ `r CT.peak.SD` days) (Figure 5) whereas overall mean peak Coho Salmon migration occurred more than a week later on `r CO.peak.mean` ($\pm$ `r CO.peak.SD` days) (Figure 6). Total number of daily captures of CCT and Coho Salmon per year are presented in Figure 6 and Figure 7, respectively. 

```{r 5. Capture Timing - Prepare fall text values, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE }
## Fall data for text
CT.first.detection.earliest <- format(min(pass.period.fall$minPass.min[pass.period.fall$Species=="CT"]), "%B %d")
CT.first.detection.latest   <- format(max(pass.period.fall$minPass.min[pass.period.fall$Species=="CT"]), "%B %d")
CT.first.detection.mean     <- format(mean(pass.period.fall$minPass.min[pass.period.fall$Species=="CT"], na.rm = TRUE), "%B %d")
CT.first.detection.SD       <- round(sd(pass.period.fall$minMeanDiff[pass.period.fall$Species=="CT"], na.rm = TRUE), 1)
CT.50p.mean                 <- format(mean(catch50prop.fall$meanDate50p[catch50prop.fall$Species=="CT"], na.rm = TRUE), "%B %d")
CT.50p.SD                   <- round(sd(catch50prop.fall$Date50pDiff[catch50prop.fall$Species=="CT"], na.rm = TRUE), 1)
CT.peak.mean                <- format(mean(catch_peak.fall$date.std_CT,na.rm = TRUE), "%B %d")
CT.peak.SD                  <- round(sd(catch_peak.fall$MeanDiff_CT,na.rm = TRUE),1)


CO.first.detection.earliest <- format(min(pass.period.fall$minPass.min[pass.period.fall$Species=="CO"]), "%B %d")
CO.first.detection.latest   <- format(max(pass.period.fall$minPass.min[pass.period.fall$Species=="CO"]), "%B %d")
CO.first.detection.mean     <- format(mean(pass.period.fall$minPass.min[pass.period.fall$Species=="CO"], na.rm = TRUE), "%B %d")
CO.first.detection.SD       <- round(sd(pass.period.fall$minMeanDiff[pass.period.fall$Species=="CO"], na.rm = TRUE), 1)
CO.50p.mean                 <- format(mean(catch50prop.fall$meanDate50p[catch50prop.fall$Species=="CO"], na.rm = TRUE), "%B %d")
CO.50p.SD                   <- round(sd(catch50prop.fall$Date50pDiff[catch50prop.fall$Species=="CO"], na.rm = TRUE), 1)
CO.peak.mean                <- format(mean(catch_peak.fall$date.std_CO,na.rm = TRUE), "%B %d")
CO.peak.SD                  <- round(sd(catch_peak.fall$MeanDiff_CO,na.rm = TRUE),1)

```

**2.4.2 Fall Return Timing**

Adult Coho Salmon have been detected at the fence as early as `r CO.first.detection.earliest` and as late as `r CO.first.detection.latest`, though most of the run (50%) arrive within a week of `r CO.50p.mean` (Figure 14 to 19). Relative to spring sampling, CCT are encountered less frequently in the fall and  arrival timing appears to be considerably more variable (Figure 20 to 22).     


#### Spring and Fall Migration Timing Tables and Figures

#### Figure 11. Spring - Overall Capture Timing
```{r 5. Capture Timing - Spring - Overall Median Capture Timing, fig.cap = "Figure 11. Overall median spring capture timing.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 6}
Spring.Boxplot.Facet
```


#### Figure 12. Spring - Daily captures of CCT per year
```{r 5. Capture Timing - Spring - Daily CT Captures per year, fig.cap = "Figure 12. Total daily capture of CCT and proportion of total annual captures.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Spring.CT)
```

#### Figure 13. Spring - Total daily captures of Coho Salmon per year
```{r 5. Capture Timing - Spring - Daily CO Captures per year, fig.cap = "Figure 13. Number of Coho Salmon captured during each day of spring fence operation since 2008.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Spring.CO)
```

#### Figure 14. Fall - Total daily captures of Coho Salmon per year
```{r 5. Capture Timing - Fall - Daily CO Captures per year, fig.cap = "Figure 14. Number of Coho Salmon captured during each day of fall fence operation since 2008.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Fall.CO)
```

#### Figure 15. Fall - Daily captures of CCT per year
```{r 5. Capture Timing - Fall - Daily CT Captures per year, fig.cap = "Figure 15. Total daily capture of CCT and proportion of total annual captures.", fig.topcaption = TRUE, echo=FALSE, warning=FALSE, message = FALSE, fig.width = 10, fig.height = 25}

print(daily_catch_plot.Fall.CT)
```




## 2.6 What are these fish doing???
```{r 8. Spring Spawners - Load Data, echo=FALSE, warning=FALSE, message = FALSE, include = FALSE}
 source("SourceFiles/8. SpringSpawners.R")
```

CCT show incredible diversity in the timing of their life history behaviours. Throughout their range, spawning has been documented in nearly every month of the year. In Puget Sound for instance, spawning has been reported from November through March and timing is highly variable between years ([Losee et al. 2016](https://afspubs.onlinelibrary.wiley.com/doi/abs/10.1080/02755947.2015.1129001#:~:text=These%20types%20of%20data%20have%20suggested%20a,coastal%20stream%20of%20southern%20Puget%20Sound%2C%20Washington.)). The spawn timing of CCT in Simms Creek is unknown, or at least undocumented, however, I would assume it occurs during a similar period to Puget Sound and is equally variable. 

The current dataset does provide some insight on spawn timing. Presumably, spawners will be >150 mm in length.

# FINISH WRITING THIS SECTION


## 3. Survival
### 3.1 What may be driving juvenile abundance
```{ 9. Survival, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
source("SourceFiles/9. Survival.R")
```

To estimate the number of Coho Salmon that survive from egg to fry, we need to make a number of assumptions:

    - All adult Coho Salmon that enter Simms Creek and all juvenile Coho Salmon that outmigrate from Simms Creek are enumerated.  
    - All adult Coho Salmon that pass the fence will successfully spawn.
    - The sex ratio of adults is equal (50% are female, excluding jacks which are assumed male).
    - Each female will deposit ~2,600 eggs.

Importantly, we also need to consider the proportion of juveniles from each age-class the emigrate each year (and assume juvenile age assignments are accurate). Fish that outmigrate as Age-0 fry will be progeny of fish that spawned the previous fall, while fish that emigrate at Age-1 would have spent a full year in the stream (i.e., spawned 2 falls previous) and Age-1+ fish would have spawned 3 years previous. Using this information, we can then calculate the total number of juveniles produced by each spawning event to calculate egg-to-fry survival.



### 3.2 What about marine survival (from smolt to spawn)

Additional assumptions are required to estimate the number of juveniles that survive to return as adults:

    - Adults spend ~18-20 months at sea (1 winter), regardless of whether they leave Simms Creek as Age-0 or Age-1.
    - Jacks return to Simms Creek after ~6-8 months at sea (0 winters). 
    - All Coho Salmon that are enumerate at the fence originated from Simms Creek (i.e., there are no hatchery fish or strays from neighbouring streams).
    



##--------------------------

```{r exit}
knitr::knit_exit()
```

##--------------------------

```{r CCT - cum.Catch.plot,echo=FALSE, warning=FALSE, message = FALSE, fig.width = 9, fig.height = 15}

labels <- data.frame(Year = unique(Spring.Catch$Year), YYYEAR = unique(Spring.Catch$Year)) %>%
          # data.frame(Year = unique(CCT_catch$Year), YYYEAR = unique(CCT_catch$Year)) %>%
          mutate(YYYEAR = ifelse(Year == 2020, "2020 - COVID",
                                 ifelse(Year == 2021,"2021 - COVID",
                                        ifelse(Year == 2023, "2023 - Strike",Year))),
                 labX = as.Date(ifelse(Year == 2020, as.Date("2024-05-25"),
                                 ifelse(Year == 2021,as.Date("2024-05-25"),
                                        ifelse(Year == 2023, as.Date("2024-05-25"),as.Date("2024-04-16"))))))
ggplot(Spring.Catch) + 
      geom_col(aes(x= date.std, y =catch))+
      geom_line(aes(x= date.std, y = prop.scaled)) +
      geom_label(data = labels, aes(label = YYYEAR),
                x = as.Date("2024-04-15"), y = 205,
                hjust = "left", vjust = 0,
                inherit.aes = FALSE)+
      scale_x_date(date_breaks = "2 week", date_labels = "%b-%d") +
      scale_y_continuous("Total Captures (# of Fish)",
                         sec.axis = sec_axis(~./300, 
                         name = "Proportion of Total Catch (%)"))+
      facet_grid(Year~Species) +
      labs(x="", y = "Total Captures (# of Fish)") +
      theme_bw() +
      theme(strip.text.y = element_blank())
    
```

```{r CCT - cum.Catch.plot2,echo=FALSE, warning=FALSE, message = FALSE }
    ggplot(CCT_catch) +
        geom_line(aes(x= date.std, y = prop, color = Year)) +
        labs(x = "", y = "Proportion of Total Catch (%)") +
        scale_x_date(date_breaks = "1 week", 
                     minor_breaks = "1 day",
                     date_labels = '%b-%d')+ 
        facet_grid(Decade~.)+
        theme_bw() +
        theme(legend.position = "bottom")



```

```{r CT Catch Summary, echo=FALSE, warning=FALSE, message = FALSE}
### Prep Data ----
CT_catch <- catch_summary %>%
            select(1:13) %>%  # Select CT Data
            pivot_wider(names_from = Period, values_from = 3:13) %>%
            select(1, ends_with("Spring"), ends_with("Fall")) %>%
            ungroup() %>%
            add_row(Year = c(2020, 2021, 2023)) %>%
            arrange(Year)


## CT Kable ----
kable(CT_catch,
      "html",
      booktabs = T,
      align = c("c"),
      col.names = c("Year","Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max",
                    "Start", "End", "# Days Sampled",  
                    "n","Med.","Min","Max", "Mean", "SD" ,"Min","Max"),
      caption = "**Table 1. Spring and Fall Trapping of CCT.**",
      digits = 1) %>%
  #column_spec(c(1, 3,10,17), bold = TRUE) %>%
  kable_styling("striped", full_width =  FALSE,
                position = "center", 
                font_size = 12,
                fixed_thead = TRUE) %>%
  add_header_above(c(" "=1, "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4,
                     "Sample Period" = 3, "Capture Timing" = 4,"Fork Length (mm)" = 4)) %>%
  add_header_above(c(" " = 1,"Spring" = 11, "Fall" = 11)) 
 
```

```{r CT Size Distribution, length-frequency all years,echo=FALSE, warning=FALSE, message = FALSE}
## Length-Frequency Plot of all CCT captured to date.
    ## Prepare Data
    CT_dat <- data_all %>% 
                    filter(Species == "CT") %>%
                    mutate(date.std =  case_when(year(Date) >= 0 ~ 'year<-'(Date, 2024))) 
                    

      ## Prepare Plot
      all_years.plot <- ggplot(CT_dat) +
                            geom_histogram(aes(x = Length), binwidth = 5, color = "black", fill = "white") + 
                            labs(x = "Fork Lenght (mm)", y = "Frequency (# Fish)") +
                            scale_x_continuous(breaks = seq(50, 450, by = 25))+
                            #scale_y_continuous(breaks = seq(0, 450, 50))+
                            theme(axis.text.x = element_text(angle = 45, vjust = 1.2, hjust = 1)) +
                            theme_bw() +
                            facet_grid(Year~.)
```

```{r compare regional trends, echo=FALSE, warning=FALSE, message = FALSE}
## Prep Regional Abundance Dataset
reg.abund <- reg.dat %>% 
                mutate(data_set = "DFO") %>%
                select(data_set, year, species, spawners, smoothedSpawners) %>%
                rename(Year     = year,
                       Species  = species,
                       n        = spawners,
                       n_smooth = smoothedSpawners) %>% 
                mutate(Species = recode(as.factor(Species),
                                                 "Coho"      = "CO_Adult",
                                                 "Chinook"   = "CN",
                                                 "Pink"      = "PK",
                                                 "Chum"      = "CM",
                                                 "Sockeye"   = "SK",
                                                 "Steelhead" = "ST"),
                                Species = factor(Species, 
                                                 levels = c("CT","CO_Adult", "CN","CM","PK", "SK", "ST")))
# Prepare Simms Data and Join with Regional Data                
catch_spring <- data_all %>%
                    filter(Period == "Spring",
                           Species %in% c("CT", "CO")) %>%
                    group_by(Year,Species) %>%
                    summarise(n = n()) %>%
                    filter(!is.na(Species)) %>%
                    mutate(n_smooth = 0,
                           data_set = "Simms") %>% 
                    relocate(data_set) %>%
                rbind(reg.abund)

catch_spring_CO <- catch_spring %>%
                      filter(Year >= 2008) %>%
                      select(!n_smooth)

ggplot(catch_spring_CO, 
       aes(x = Year, y = n)) +
  geom_point() + 
  geom_line() + 
  facet_grid(Species ~., scales = "free")

catch_spring_long <- catch_spring_CO %>%
      select(!data_set) %>%
      pivot_wider(names_from = Species, values_from = n) %>%
      drop_na()

cor(catch_spring_long)
```

# 3. Fall Fence Operation
### 3.1. Monitoring Effort



